Practical Optional Types for Clojure

### 2018-05-18 overview.tex
typo

\begin{exmp}
\begin{lstlisting}
(*typed ann desserts [Order -> Int] typed*)
(defmulti desserts :Meal)  ; dispatch on :Meal entry
(defmethod desserts :lunch [o] (*invoke :desserts d invoke*))
(defmethod desserts :dinner [o] (*invoke :desserts d invoke*))
(defmethod desserts :combo [o] 
  (*invoke + (*invoke desserts (*invoke :meal1 o invoke*) invoke*) (*invoke desserts (*invoke :meal2 o invoke*) invoke*) invoke*))

(*invoke desserts {*map :Meal :combo, :meal1 {*map :Meal :lunch :desserts 1 map*}, 
           :meal2 {*map :Meal :dinner :desserts 2 map*} map*} invoke*) ;=> 3
\end{lstlisting}
\label{example:desserts-on-meal}
\end{exmp}
%
The \clj{:combo} method is verified to only structurally recur
on \clj{Order}s. This is achieved because we learn the argument \clj{o} must
be of type
\clj{'\{:Meal :combo\}}
since
\clj{(isa? (:Meal o) :combo)}
is true. Combining this
with the fact that \clj{o} is an \clj{Order}
eliminates possibility of \clj{:lunch} and \clj{:dinner}
orders, simplifying \clj{o} to
\clj{'\{:Meal ':combo :meal1 Order :meal2 Order\}}
which contains appropriate arguments for both recursive calls.

>>>>

\begin{exmp}
\begin{lstlisting}
(*typed ann desserts [Order -> Int] typed*)
(defmulti desserts :Meal)  ; dispatch on :Meal entry
(defmethod desserts :lunch [o] (*invoke :desserts o invoke*))
(defmethod desserts :dinner [o] (*invoke :desserts o invoke*))
(defmethod desserts :combo [o] 
  (*invoke + (*invoke desserts (*invoke :meal1 o invoke*) invoke*) (*invoke desserts (*invoke :meal2 o invoke*) invoke*) invoke*))

(*invoke desserts {*map :Meal :combo, :meal1 {*map :Meal :lunch :desserts 1 map*}, 
           :meal2 {*map :Meal :dinner :desserts 2 map*} map*} invoke*) ;=> 3
\end{lstlisting}
\label{example:desserts-on-meal}
\end{exmp}
%
The \clj{:combo} method is verified to only structurally recur
on \clj{Order}s. This is achieved because we learn the argument \clj{o} must
be of type
\clj{'\{:Meal ':combo\}}
since
\clj{(isa? (:Meal o) :combo)}
is true. Combining this
with the fact that \clj{o} is an \clj{Order}
eliminates possibility of \clj{:lunch} and \clj{:dinner}
orders, simplifying \clj{o} to
\clj{'\{:Meal ':combo :meal1 Order :meal2 Order\}}
which contains appropriate arguments for both recursive calls.
